cvx-flats

### 2020-05-22 neurips-20/cvx-flats.tex
Finishing touchups post Monday meeting.  Passed over Lemma 2 with Bo this morning and more changes are coming.

\begin{definition}[Consistent: property]\label{def:consistent-prop}
  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.  We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere. \jessie{Changed}}
  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ any function where $\propdis(r,p) = 0 \iff r \in \gamma(p)$.

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer. \jessie{Don't need anymore now that we're using Lemma 5 anyways.}}
\end{proposition}
\begin{proof}
%	\jessie{Intuition: Contrapositive.
%		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
%		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
%		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
%	}

	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Take $D$ to be the distribution with conditional probability $p_y(x) = Pr[Y = y | X = x]$, and let $p$ be the distribution conditioned on $x$.
	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
  \raft{Type error with $D=D_x$; see AA15 for how they phrase}
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
\end{proof}

@@

	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, a distribution $D$ with point mass on $x$ and $D_x = p$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
  \raft{Check $D$ wording here too}
  	Since $\{u_m\}$ is a constant sequence, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
%  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) \not \to 0$ as $\propdis(\psi(u), p) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
\end{proof}

@@

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  To spell it out, observe $F-p$ is a subspace as it is a linear transformation of $F$, which is a subspace by definition of a flat.

  Now consider $q \in F - p$.
  First, if $p+q \in \gamma_r$ and $p -q \in \gamma_r$, then we have $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
  If either $p + q$ or $p - q \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.

  However, if both $p + \alpha^+ q$ and $p - \alpha^- q \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $q \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $q \not \in F - p$.
  Therefore, we have $q \in F - p \implies q \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
\end{proof}

>>>>

\begin{definition}[Consistent: property]\label{def:consistent-prop}
%  \raft{You have $\mu$ and $\mu^\gamma$; I'd vote just $\mu$.  We'll want to change $\mu$ to something else eventually anyway, so maybe a macro unless we're sure $\mu$ won't show up elsewhere. \jessie{Changed}}
%  \raft{Maybe clearer this way: Introduce $L,\psi,\gamma$.  Then intro $\mu$ as any such function.  Then the def. \jessie{Done}}
	Suppose we are given a loss $L : \R \times \Y \to \reals$, link function $\psi: \R \to \R'$, and property $\gamma:\simplex \toto \R'$.
	Moreover, let $\propdis : \R' \times \simplex \to \reals_+$ any function where $\propdis(r,p) = 0 \iff r \in \gamma(p)$.

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
\end{proposition}
\begin{proof}
%	\jessie{Intuition: Contrapositive.
%		Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
%		Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
%		Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
%	}

	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
  \raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
\end{proof}

@@

	Consider the constant sequence $\{u_m\}$ with $u_m = u$ for all $m$, and take $D \sim \X \times\Y$ with only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D g(X,Y) = \E_p g(x, Y)$ for all functions $g : \X \times \Y \to \reals$, and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
  \raft{Check $D$ wording here too \jessie{better?}}
  	Since $\{u_m\}$ is a constant sequence, we observe $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$ since $u \in \Gamma(p)$.
	This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$.
%  \raft{Maybe clearer to first say $\E_D L(f_m(X), Y) = \inf_f L(f(X),Y)$ for all $m$, and then the easy implication of the convergence \jessie{Done}}
	However, we have $\E_X \propdis(\psi \circ f_m(X), D_X) = \propdis(\psi(u_m), p) \not \to 0$ as $\propdis(\psi(u), p) \neq 0$ (since $\psi(u) \not \in \gamma(p)$) and the sequence is constant.
%  \raft{Almost -- just clarify that this is the expectation over $D$ too by construction \jessie{Kinda done?}}
	Thus, we observe $(L, \psi)$ is not consistent with respect to $\gamma$ (Definition~\ref{def:consistent-prop}).
\end{proof}

@@

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a subspace by definition of a flat.
  Now consider $v \in F - p$.
  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the same affine space as $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
%  
%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
%  Therefore, we have $v \in F - p \implies v \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
\end{proof}
